\chapter{Year 1985}
\label{1985}

\section{June 26--July 9: Ibiza (Cala Azul)}
\label{1985:Ibiza}

The first bits of holidays I remember are from Ibiza. There were beaches, lots of little stones, which you could use to built ``high'' castle mountains (aka a couple of cm). My favourite toy car -- an Unimog -- lost its front tyre. I blamed that on my sister (nobody remembers if she was actually in any way responsible though). Oh and if you should be looking at the year itself, indeed I am not the youngest spring chicken in the world anymore.

\chapter{Year 1987}
\label{1987}

\section{Summer: Mallorca (Calas de Mallorca)}
\label{1987:Mallorca}

Another summer outing to Spain, this time with a DC10 from Zurich. My parents though a king size bed could be enough space for the kids to be happy. Unfortunately for them their three kids who were supposed to share the bed didn't think so, thus continuously hitting and beating below the pillows. As consequence we had to get into bed in shifts. The beach was quite some distance away, so we had to take the bus to get there. The hotel pool was nice at least for us kids. My dad and I also checked out a larger pool which was close-by. Clearly targeting families there was also a kid's disco, where we spent out evenings at. We also collected shells by the beach. We also went to a little bird zoo. The highlight was the Cuevas del Drach (at least for me as kid). The cave has a lot of Stalactites and Stalagmites all over, and an underground lake where boats are running on surrounded by classical music. Little me was impressed. By the way should you miss the year 1986, I have no memory or idea what was going on in that year, for sure we went somewhere doing something but even I can forget things.

Cuevas del Drach*****, Bird Zoo***

\section{October 24-31: Flumserberg}
\label{1987:Flums}

There was a time, when Switzerland was not that amazingly more expensive than the rest of Europe. In those times my parents decided it would be nice to spend some late Autumn days in the alps around Flumserberg. I don't have that many memories of the trip besides the following: Almost every morning the valley was covered in fog, and we had clear skies up over all of this soup of condensed water. Then my parents took us to the Tamina Gorge - or well, that was the actual plan. But seems due to heavy rainfalls the days before, the gorge had already closed its gates. Thus we had to turn back, but collected chestnuts and Slate tablets on our way back, which were then put together into animals to play with, or drew on it with chalk. We also looked for knights in the castle of Sargans. Unfortunately there weren't that many of them around anymore. We also hiked up to the Heidi Alp, in fact the Heidi movies had been shot there, and the place had inspired the famous Japanese Heidi anime as well. Besides the hike we kids were more interested into the helicopter transporting trees down the valley. We also took a gondola up the mountains, where we did long hikes (I am sure they were actually not that long, but for the kid of me they seemed long). \\

Heidialp hike****, Sargens Castle***

\chapter{Year 1988}
\label{1988}

%horn, July 
%aachquelle, hohentwiel, lake constance, unteruhldingen

\section{October 24-October 29: Beatenberg}
\label{1988:Beatenberg}

%truemmelbach, Grindelwaldgltscher, Aareschlucht
Another year, another holiday spent in Switzerland, this time in Beatenberg which is a village overlooking a cliff of Lake Thun. Being opposite of Jungfrau you have quite a view of the Berner Dreigestirn -- Eiger, M"onch, and Jungfrau. Now there is also a chair lift going up the close-by mountain, the Niederhorn, which we had to see too. Most of the days we spent in the indoor swimming pool or in the kindergarden which was part of the hotel complex. We also visited the waterfalls of Tr\"ummelbach. I remember more of the lift through the mountain than the actual waterfalls though. We also visited the glacier cave of the Upper Grindelwaldglacier. For me it was very impressive to talk through the ice to reach the cave. 1988 is roughly the time when the glacier reached one of its maxima over the last 500 years, it was very impressive to see. Unfortunately by now the glacier tongue retreaded quite substantially by a couple of kilometres, it cannot be seen from the valley anymore and it is so far less accessible that people gave up on carving a glacier cave over a decade ago. Even climbing up several ladders and crossing the glacier gorge doesn't even get you to the dead ice formed by the nowadays detached lower tongue below the once existing second lower icefall of the glacier.\\

Tr\"ummelbach Waterfalls*****, Upper Grindelwaldglacier Cave*****


