\chapter{Year 1989}
\label{1989}

\section{May: Beatenberg}
\label{1989:Beatenberg}

%ballenberg here

Another morning we went to the Beatus caves, one of the larger caves in Switzerland with an entrance just next to a waterfall. I remember we did a longer hike, and we walked over meadows with lots of cows on. My mum reminded us that we should stay away from cow poop, but she used the dialect word (Kuhdeitsche), which I never had heard of. So I asked her what that stuff is, notably just stepping into the cow shit at that very same moment. Clearly mum wasn't too happy, even my younger brother who was just 2 years old at that point can tell that story. Anyways the hike went on for longer and longer and longer, thus my parents decided to cut it short and take the bus back at the first occasion without getting to the place which was originally foreseen as destination\\

Beatush\"ohle**** and close-by waterfall****

\section{June: Horn}
\label{1989:Horn}

What can you do with young kids: what about camping by a lake. My dad, my older brother and I built the tent (I doubt I was really that much of help). Clearly it was a nice setting with the camping ground distributed throughout a forest area, where we could play or let snails run against each other. On the other side the camping ground was very close to the lake with a sand beach. We did also go to Reichenau by boat, where we also the churches. I remember I was particularly impressed how large the Minster was (in fact it is not all that large, but having had not seen any large church at this point, I didn't know that). We also went to Meersburg to see the Zeppelin museum with many models and also burnt remains of the LZ129 Hindenburg. Clearly I became a fan of air ships and Zeppelins in particular for a while. We also visited the Old Castle (Altes Schloss), which has some of the oldest and mightiest walls from medieval times in Germany. And last but not least we visited Hohenzollern, the original family seat of the former Imperial family. In fact most of the castle is a neogothic interpretation of the old castle from the 19th century, when the castle was rebuilt after centuries of decay. Only one chapel is in fact from the medieval era. I liked the slippers they gave us which were fun to slide over the floors.

Reichenau: churches****\\
Meersburg: Zeppelinmuseum****, Altes Schloss***\\
Hechingen: Hohenzollern Castle***

%missen willams November  --> Wanderung lost in woods, Nebelhorn
\section{November: Missen Willams}
\label{1989:MissenWillams}

In 1989 we even did a third little holiday, this time in the Allg\"au region in the German state of Bavaria in a place which had two floors, the upper room just below the roof was my and my older brother's room. We did mainly walks and hikes in the forest. On one of those hikes we messed up and took the wrong turn at one point. Realising that the hike didn't lead to our originally foreseen place, my parents decided to cross the meadows and just to try to get down to the valley again, and clearly we made it back to the hotel after that detour. The highlight of the trip was our cable car ride up the Nebelhorn by Oberstdorf where we enjoyed the mountain panorama and got some Schupfnudeln.\\

Oberstdorf: Nebelhorn****