\chapter{Year 1990}
\label{1990}

\section{May 25--June 8: Ibiza}
\label{1990:Ibiza}

What I didn't know back then: This marked the last flight for a while, taking a Belair DC9 to get to Ibiza and back. This time we stayed in San Antonio. I don't remember that much of the trips, but we were part of the daily morning jogging animation, as well as hanging around the pool. There was a daily kid's disco with some games being played (which was one by my little brother). Then we also participated in a treasure hunt where we had to split into teams. This time my sister's team won. She wasn't that happy that her team won biscuits while we others (as loosers) won bonbons. I was responsible for watering the plants on the roof terrace and the balcony. We also went to church once, I was surprised how the Spanish children were allowed to run around without anybody telling them to sit down and behave. Clearly there was a lot more of singing going on that in Germany, not that I understood any of it. This time the beaches were small but nice (and also close) with lots of seashells, and also fish swimming around. At some point we had dinner somewhere in the middle of the island - for sure chicken was part of the menu. I also wrote my first postcard to my godmother, going for a postcard depicting fireworks over the citadel of Ibiza City. Well things one does, once one learnt how to read and write (in some countries kid's start school kinda late). Ibiza City was also the only major tourist sight we did, climbing up all the way to the top of the citadel and the cathedral. From there we had a superb view of the harbour and the huge car ferry, at least I thought back then it was huge. For once my older brother and I had our own room with a bathroom attached (yes we were the big kids).\\

Ibiza City: Citadel \& Cathedral***

%August: Habsburg, Wildegg (zu)
%August: Einsiedeln

\section{October 27--November 3: Lechbruck}
\label{1990: Lechbruck}

%28 Lechsee
%29 Hohenschwangau, Neuschwanstein
%30 Patrozinium Lechbruck
%31 Wieskirche (renovation)
%1 Auerberg (moving clouds, church), Bernbeuren (church)

The first of two visits in Lechbruck which is home of a holiday village where each family can rent a small house. It is close to a natural small pond in a forest and only a short walk away is the local indoor swimming pool with an attached hot pool outdoors (don't know if this is from a real thermal spring though). The town of Lechbruck is next to the reservoir of Lechsee, which is nice for some walks. Close by is the Auerberg with a pilgrimage church on top. I enjoyed particularly the fact that one could just lie in the grass on the mountain top and see how the clouds move just by looking up the church tower. Then we visited the Wieskirche, but I only remember all the scaffolding of a large renovation campaign at that time and not much more. A highlight of the trip was a visit of the Hohenschwangau and Neuschwanstein castles. I remember I even enjoyed the visit of Hohenschwangau more, feeling all the history of knights around me (in fact the castle is though a neogothic rebuilt of a much older medieval castle).\\

Schwangau: Hohenschwangau*****, Neuschwanstein****
Lechbruck: Lechsee***
Steingaden: Wiekirche (in renovation)**
Bernbeuren: Auerberg Hike \& Auerberg Pilgrimage Church****