\chapter{Year 1993}
\label{1993}

\section{October 30--November 6: Telfs}
\label{1993:Telfs}

The house was really nice, my brother and I had the basement all for us. In the morning the Hohe Munde mountain greeted us through a large window. The pool was decent enough (with a hair dryer that only blew a bit of warm air out, but didn't dry in any useful way).
The highlight was the visit of Zugspitze from the Austrian side via a cable car from Ehrwald. From there we could also walk over to the German side (after all the mountain is the tallest one in Germany). I also realised i would need stronger glasses once i ran into a glass door not realising it was shut. On the way back we stopped by the Fernstein mountain pass, walking around the lake and visiting the Sigmundsburg on the peninsula.\\
By Stams is a large Baroque monastery with a giant gilded wood carved main altar. Close-by is an old suspension bridge leading over the green waters of the Inn and a nice waterfall.\\
We also visited Innsbruck with its beautiful Baroque cathedral (surprisingly there are many Baroque style cathedrals in Austria unlike in Germany, where gothic style is dominating). Interesting to visit is also Hofkirche, where the emperor had a tomb constructed with life size bronze statues of ancestors and family members (as far as I know his body isn't in the tomb though). The Imperial palace of Hofburg was largely remodelled in Baroque times for a royal wedding, the large Riesensaal (Hall of Giants) has huge frescoes and paintings on the ceiling and the walls. We saw more churches in the Wilten suburb, had more little hikes to old ruined castles, and did tour a silver mine by Schwaz, visited then the parish church and had fish nuggets and fries.
Not to forget: since everybody could choose something to do, my older brother wanted to go to McDonalds. Thus this was my first time I had McDonalds food, he didn't know that in a couple of future trips that would be my Mum's default to go to if she was very hungry or needed a large drink.

%Hohe Munde, 30 pfarrkirche
%31 Zugspitze, Fernstein Sigmundsburg
%1 Stams, zugbruecke
%2 Insbruck Dom Hofburg, Hofkirche
%3 Burg Hoertenberg
%4 Schwaz, Wilten, McDonalds
%5 Telfs Kirchen
