\chapter{Year 1995}
\label{1995}

\section{August: Seepark Kirchheim}
\label{1995:Kirchheim}

The last trip I did without having a camera myself. We stayed at the Seepark Kirchheim resort, a holiday village next to a lake in Kirchheim. Clearly having a lake is very nice for swimming in hot summer days. Kirchheim is very close to Bad Hersfeld which is famous for its large ruined Romanesque abbey, one of the largest in Germany. But it is also very close to Eastern Germany. After the fall of the wall and later reunification this was my first time in this part of Germany. Many infrastructure works had been going on at that time, but old cobble stone was still the main road surface in the inner parts of the towns. We did see the Wartburg castle in Eisenach and the impressive cathedral in Erfurt. In Weimar we only walked around and saw Goethe's and Schiller's houses, but I was not too impressed at that point. I did enjoy a trip to Fulda with its large Baroque cathedral. In Frankfurt I was particularly impressed by its skyline. Not many towns in Europe had proper skyscrapers at that point, and the banking district of Frankfurt was very unique in that send. I was a bit disappointed by Paulskirche, it is more famous though as the meeting place of Germany's first elected parliament back in 1848. The Dom in Frankfurt has in fact never been the seat of a bishop, but it has been the coronation church of the German emperors several times,\\\

Erfurt: Dom*****\\
Weimar: Old Town with G\"othe and Schiller House**
Eisenach: Wartburg*****\\
Bad Hersfeld: Abbey****\\
Fulda: Dom*****\\
Frankfurt: Dom***, Paulskirche**, Flughafen (Plane Spotting)****