\chapter{Year 2003}
\label{2003}

\section{July: Bodrum}
\label{2003:Bodrum}

Gianrico, Sigi, B\"oni and I wondered where we should relax after our hard first year physics exams at ETH. Back then we had to go through catalogues to find suitable places. My mum suggested that maybe we could go to Turkey, and why not to Bodrum. We were easily convinced and ready for some days by the beach.\\

Co-travellers:\\
Gianrico, Sigi \& B\"oni: just like me first year undergrads studying physics at ETH Zurich.\\

My dad volunteered to pick everybody else up in Zurich and drive us to Stuttgart airport. Apparently the three of them had already a wild evening, B\"oni at least thought it was a brilliant idea to have a few drinks to forget about his flight fright. We also passed a couple of accidents on our nightly drive to Stuttgart. We arrived well in time, even the check-in lines were not operating yet. On the flight we met my local village's political figureheads who went on a sailing trip in Turkey. After a short stop at another airport we finally arrived in Bodrum and took a small bus to our resort. It was indeed very nicely located, overlooking the sea and a small island, a bit removed from the city with a large pool and a small apartment with two bedrooms. Since our all inclusive package included all kind of drinks we had a pretty good time by the pool, on the bar, as well as checking out the beach. Gianrico unfortunately caught an ear infection, thus he was not allowed to really dive deep into the pool anymore. On our first day we wandered through Bodrum and opted for a night out on a club boat. We soon found out that the music was not really suited for our style, but then we were stuck on the boat for more than 3 h anyway. In our club we also had a couple of nice late evening concerts, which I enjoyed quite a bit, same with the sunset over the mountains. Unfortunately on one day we were affected by one local wildfire which ravaged for about a day before they managed to put it out. Getting back into Bodrum frequently for dinner and night activities we found a nice bar just by the sea with nice views of the old harbour and the castle. Since it was a nice time out with music according to our taste we went there about three times, each time meeting the same fun dutch ladies as well. For our cultural program we visited the close-by ruins of Ephesus with the famous theatre and the breathtaking library, the merchant houses were just opened, but we didn't go to those. On our way back we had a short photo stopped by the one remaining column of the temple of Artemis, which is in fact patched together using fragments from different columns. Although I knew that Bodrum is the former site of the Mausoleum of Halikarnassos (another one of the former ancient wonders of the world), we didn't see the local archaeology museum either. Overall we had a lot of fun swimming, eating good food and having a couple of drinks day in day out. Well-needed after the stressful examination period.\\

Ephesos***\\