\chapter{Year 2004}
\label{2004}

\section{March 2004: Frankfurt}
\label{2004:Frankfurt}

My dad had a business meeting in Frankfurt. Being on spring break without any exams following (these happen at ETH only in Summer, unless you have to repeat exams), I decided to join him, or rather join him on the road to Frankfurt, and then go on my own way. What can you do in Frankfurt: besides seeing Paulskirche, the first meeting place of an elected parliament in Germany, and the Dom, the former coronation church of German Emperors, there is the Bankenviertel. The only business district in Germany with plenty of skyscrapers, the tallest one in Germany and some of the tallest in Europe. But other than that Frankfurt is just a big city, without that much more to do

\section{July 2--July 9: Tunisia}
\label{2004:Tunisia}

How this trip came into existence: After studying real hard for another year, we decided to go on another beach holiday. This time we followed recommendations from Sigi's mum and ended up in Tunisia. Fan fact: my sister thought it looks awesome as well, and booked the same resort with her friends a week later.\\

Co-travellers:\\
Sigi and Gianrico: having shrunk after B\"oni's departure after last year's examination this time we booked a larger room for three wild physics students from the holy trinity of Germany (myself), Switzerland (Gianrico), and Austria (Sigi).

Unfortunately I don't have particular dates recorded for this trip, besides the fact that there were two pools in the resort, a large disco, which came in handy, after we found out that the bars and clubs in Sousse and Monastir were not on par with those we encountered in Bodrum the year before. On the first day we made our way to Sousse, with its old city walls and Medina, but after a nice dinner all music we could hear were more traditional and the city was more tame than Bodrum, thus in the next few days we always stayed at the resort and enjoyed the disco there.\\
The pool was nice too, this time nobody had to suffer through an ear infection. But the best was still to come: two or three days in we got hit up by a german Neckerman employee Heike: She asked us, if we wanna join. We were -- alright, join what -- Getting totally SMASHED! -- Ohhh, well, no, thanks, but no. Seems that was not really the expected reaction: ``What, i don't understand, you don't wanna get drunk and puke all over -- you are on holidays, you can see an authentic tunisian show - with me fire-spitting'' (clearly authentic). ``We even don't care if you throw up in the bus, even that is fine. And you still don't want to come and get smashed''. We must have been the strangest young people to her, and nope we didn't join her.\\
We had though one dinner at a restaurant, where they serves us all vine we wanted. Clearly splitting two bottles between the three of us, wasn't the smartest idea we had, but considering we stayed in the resort nothing much happened otherwise. Clearly we also did a trip to see other places in Tunisia, notable the capital Tunis itself, visiting the really nice , and then we went on to the ruins of Carthage. Little is left from the punic times, besides a few findings put in museums, but the romans built up quite a sizeable again, particularly the Roman Baths were impressive.\\

Carthage: Excavations****\\
 Tunis: Medina with National Museum*****\\
 Sousse: Medina***

\section{October 15--October 20: London}
\label{2004:London}

Learning for this year's exams Gianrico realised on this weekend the last easyjet flight to London (actually London Luton) would fly (they did come back later on though). Thus he decided we couldn't let such an opportunity go by, and booked tickets.\\

Co-travellers:\\
This time it was four of us: Gianrico, myself, Sigi, and Anne, a ETH math student in our year from Luxembourg, who happened to be Sigi's girlfriend too (so clearly two rooms it was for this trip):\\

Unfortunately once again I have no detailed recollection of when we went, besides the fact that it was after the ETH examination period, and most probably late September. We started our trips with the Dinosaurs at the museum of natural history. We also did pay a visit to the British Museum (amazing as always). Our tourist programme was rounded of with the Tower of London and St Paul's. Now this trip wasn't supposed to be cultural only: The first night we decided to spend at the club of the Swiss house by Leicester Square: but that R\&B music (Destiny's Child etc etc), wasn't so much to our liking. The next days we went to other dance clubs, playing rather dance and pop music (or a pop cover night for that matter). After all it is great to dance until 3 or 4 am the next day. By coincidence while waiting at the half fare ticket booth, we realised there were so many people waiting all over, and we found out pretty quickly, that it was the premier of ``Finding Neverland'', and indeed we later saw Johnny Depp and Kate Winslet walk by and shaking hands with fans.\\

London: Museum of Natural History*****, Tower of London****, St Paul's Cathedral*****, British Museum*****
