\chapter{Year 2021}
\label{2021}

\section{January 10: Bad S\"ackingen \& Laufenburg (Baden)}
\label{2021:BadSaeckingen}

After December was a stay at home months, I finally got out with my dad, staying close to home though, first visiting the town of Laufenburg. Their advertisement slogan is one town, two countries. Historically the town of Laufenburg has a centuries old history together before Napoleon decided to redraw borders separating the town in the middle. The larger part of old town with a ruined castle is in Switzerland nowadays. Usually one can just walk across both parts of the city, but nowadays with the government in my German state deciding walking over the border is not allowed without quarantining we didn't do that. Instead we continued our short afternoon outing in S\"ackingen. Home to a nice Rokoko church which used to belong to a monastery, the Fridolinsm\"unster. Usually on a nice beautiful day like this many guests, also from the Swiss side might have enjoyed a walk or cafe, but right now that isn't an option either, we did walk a bit on the Wooden Bridge, in fact the longest wood covered bridge in the Europe beating out Kapellbr\"ucke in Luzerrn by a few metres. Clearly not allowed to cross over we turned around midway as well.\\

Bad S\"ackingen: Wooden Bridge****, Fridolinsm\"unster****\\
Laufenburg (Baden): Old Town***\\

\section{February 4: Aach \& Reichenau}
\label{2021:AachReichenau}

It had been raining heavily and snow was melting too, rivers were really might on that day. Even the little creek of Aitrach looked more like a river and the Danube had crossed over its dams in some spots. The Aachtopf is Germany's largest karst spring, fed by water originating from the Danube sinkhole where the Danube itself disappears for about two thirds of the year (clearly not the case during snow melt). The spring is impressive forming a little lake just by a hill side. Since we were in that area we continued to Reichenau in order to see the first UNESCO world heritage site of 2021 (if you follow the past years you realise it appears pretty often on that list). This time my dad and I started at St Peter and Paul, continued with the Monastery, ending in the highlight of St Georg. I always enjoy seeing all those old churches and their early medieval frescoes. Unfortunately this time around we were not able to stop in any cafe to get some coffee or cake, clearly all of those had been closed too.\\

Aach: Aachtopf**\\
Reichenau: St Peter \& Paul****, Monastery****, St Georg*****\\

\section{February 6: Lake Constance Area}
\label{2021:LakeConstance}

Uhldingen-M\"uhlhofen: Pilgrimage Church Birnau****\\
Lindau: Minster***, St Peter***, Harbour with Lighthouse and Bavarian Lion****\\
Weingarten: Abbey****\\
Meersburg: Old Town****

\section{February 14: Haselbach Falls}
\label{2021:Haselbach}

After about a week of not going outside, I convinced my dad to do one of the quick walks close to the area, thus we drove the few villages up to Indlekofen and walked down the little valley of Haselbach. The trail had been refurbished just in Fall 2020 and we made use of those new fences on the slippery icy patches of the path. The Haselbach creek falls down in several cascades with the largest drop by the Haselbachfall which is 14 metres high. The trail crosses the creek on three occasions. Thus you get a view of the waterfall from above and below. At the time of our visit due to the cold temperatures of the preceding days parts of the waterfall had been frozen. Also a tree had fallen and got stuck in the middle of the fall. Not a bad experience for a 45 minute long walk.\\

Waldshut-Tiengen (Indlekofen): Haselbach Falls***

\section{February 19: Schl\"uchtsee}
\label{2021:Schluechtsee}

What do you do if you want to enjoy a nice afternoon in the region: what about going to one of the multiple little small mountain lakes. The Schl\"uchtsee is a very small reservoir, set up originally as ice lake for the close-by Rothaus Brewery. The lake is about 5 m deep, in mid February the lake was completely frozen, but pretty idyllic walking around it (the trail is not more than 2 km long). The lake is within a forest area, the Schl\"ucht river begins just a bit beyond it flows into the lake. Typically one can have beers or wine in the farm close to the lake or in summer just jump into the water having a short swim. It is a nice place for families with small kids, but not really anything special to be honest.\\

Grafenhausen: Schl\"uchtsee***

\section{February 21: Beuron and Upper Danube Canyon}
\label{2021:Beuron}

Beuron: Monastery****, Upper Danube Canyon*****\\
Sigmaringen: St Johann***

\section{February 23: Roggenbach Castles}
\label{2021:Roggenbach}

Bonndorf: Roggenbach Castles***

\section{February 26: Menzenschwand \& Todtnau}
\label{2021:Todtnau}

St Blasien (Menzenschwand): Albklamm \& Menzenschwand Falls****\\
Todtnau: Todtnau Waterfall*****

\section{February 27: Freiburg \& Black Forest}
\label{2021:Freiburg}

Breitnau: Ravenna Gorge*****\\\
Freiburg: City Gates**, Minster******\\
St Peter: Monastery****\\
St M\"argen: Monastery****\\\
Titisee-Neustadt: Titisee***\\
Lenzkirch: Windgf\"allweiher****\\
Schluchsee: Schluchsee***

\section{February 28: Rickenbach}
\label{2021:Rickenbach}

Originally the plan was to go to the ruined castle of Wieladingen first, and then continue via the Lehnbachfalls along the Murg river with its waterfalls up to the Strahlbrusch waterfall. It was possible to get to the cascades of the Lehnbach creek, but the bridge crossing the river at that point had been damaged by fallen trees a couple of days previously. Thus one had to get to the castle via a different route crossing the creek a bit below. The castle itself had been renovated a couple of years before, from the belfry one can see up to the Swiss Jura (the alps were not visible then), and up the Murg valley on the other side. Unfortunately the way along the Murg had been closed as well. Thus we drove up to another parking lot, and start our second hike from there. This hike led alongside an old abandoned quarry and passing the Seelbach creek down to the Strahlbrusch waterfall. The waterfall is about 12 m high, and in snow melt pretty strong as well. We crossed the Murg via an old bridge of an old postal route which also crossed two small tunnels. Since the trail was closed on this side, we just turned back to the car. All in all a nice afternoon out but for sure the Murg canyon itself could have been a nice hike too, but if it is closed due to snow or rock falls you rather don't risk it.\\

Rickenbach: Castle Ruin Wieladingen***, Strahlbrusch Waterfall****

\section{March 2: G\"orwihl}
\label{2021:Goerwihl}

G\"orwihl: Aybach Waterfall***, H\"ollbach Waterfalls****

\section{March 6: Constance \& Hegau}
\label{2021:Konstanz}

Constance: St Stephan***, Minster*****, Christ Church**, Holy Trinity Church**\\
Hilzingen: Hohenkr\"ahen****\\
M\"uhlhausen: M\"agdeberg****\\
Tengen: Hinterburg**, M\"uhlbach Gorge***

\section{March 9: Waldshut}
\label{2021:Waldshut0309}

In Waldshut the Wutach river finishes its flow by the Rhine river. Recently a lot of work had been going into making the mouth appear more natural and less canal like. Thus islands had been created with a second small arm of the Rhine as well as an area where the Wutach river can overflow in case of high water. Only a months ago snow melt was happening but already in March the second high water arm had retreated leaving only muddy but pretty dry territory.\\

Waldshut: Wutach Mouth**\\

\section{March 25: Triberg \& Villingen}
\label{2021:Triberg}

Triberg: Triberg Waterfalls*****, Schonach Waterfall***\\
Schonach: first world's largest cuckoo's clock**\\
Villingen: Johanniterkirche**, City Walls and City Gates***, Minster***

\section{March 28: Alb gorge}
\label{2021:Albtal}

Dachsberg: Alb with Teufelsk\"uche (Devil's Kitchen)****\\
G\"orwihl: Krai-Woog-Gumpen and Gletscherm\\"uhle***\\
Gutenburg: Teufelskessel waterfall***

\section{March 30: Blumberg, Mundelfingen \& Immendingen}
\label{2021:Blumberg}

Blumberg: Schleifenbach Waterfalls****\\
Mundelingen: Mundelfinger Waterfall \& Aubach Gorge**\\
Immendingen: Donau Sink Hole** (too much water at this time of the year), H\"owenegg with crater lake****\\

\section{April 11: St\"uhlingen \& Grimmelshofen}
\label{2021Stuehlingen}

I had been in St\"uhlingen multiple time on carnival parades, music festivals, or just as final destination of bike rides in my teenage years. It had been a while though since I saw old town with the city church, and the church of the Capuchin monastery. Then we continued our trip to the small village of Grimmelshofen, walking along the Wutach and going down to the Dampfkessel waterfall, not as mighty e.g. as the Lauffen waterfall in my home village, but 2-3 m are not nothing either. On the way back we drove past the Hohenlupfen castle and took a panoramic route to Bonndorf enjoying some views of the snow covered alps in the distance.\\

St\"uhlingen: old town***, panoramic road with view of the Alps***\\
Grimmelshofen: Dampfkessel waterfall***

\section{April 20: Hohentengen}
\label{2021Hohentengen}

Another close place to home is the village of Hohentengen, originally home to three castles. Out of those one has been completely destroyed, on that spot there is now a Swiss army bunker. The second castle of Weisswasserstelz is in ruins nowadays too, a few walls remain though, which give you an idea of the former glory. Rotwasserstelz Castle still guards the bridge over to the Swiss town of Kaiserstuhl. But in April 2021 borders are forbidden to be crossed.\\

Hohentengen: Rotwasserstelz Castle**, Ruin Weisswasserstelz**

\section{April 24: Kaiserstuhl \& Breisach}
\label{2021Kaiserstuhl}

Bickensohl: L\"ossholweg hike****\\
Breisach: oldtown with Stephansm\"unster****

\section{April 28: Moving to Vienna}
\label{moveVienna}

At some point also physicists leaving academia find jobs: I found my first job in Vienna. Since the pandemic was still going on (3rd wave now), it all was followed by a quarantine protocol. Since I received the green light for my flat by the very end of April (26 to be precise) and I wanted to avoid being caught up in delayed administrative procedures due to the pandemic I jumped almost immediately on the next available train with two suitcases while packing up and organising the move of all my personal belonging with a company over a week later. Quarantining alone with a limited data package, no TV, and no radio (but two books) is tiresome. This is the time when you realise how much your interactions with friends mean to you, while also living through the downsides of single life.

\section{2021: Vienna general}
\label{2021Vienna}

Considering that I live in Vienna now, the city drops out of touristic trips and travel for the time being. Nonetheless it is clearly a place to visit with many spots to see. Instead of now being silent about all of that from the following on, I decided to collect per year all information gathered within each year in order to keep track of new developments or just to describe what there is to do (or on the other hand what you should avoid doing).\\

Now what about nature: what many people are not aware of is that in Vienna you even have parts of an Austrian national park: The Donau Auen. Around Vienna the Danube river was left largely unregulated for many centuries. By now the river has been corrected and regulated. One arm is the canalised Donaukanal, the former main arm has no connection to the Danube anymore but exists as lake called Alte Donau. Other side arms are now fed by ground water and rain without being connected to the main river anymore. A lot of reed is growing in those low water and only partially flowing old arms. Nowadays plans are put up to divert periodically a bit of water from the Danube to keep the eco system alive and full, in some parts the arms had been reconnected by now. Anyways you find many wetland typical plants, animals such as frogs, fish, insects all over the are in a forest scape. A grid of walking trails and bike paths has been set up on both sides of the river.\\
From the churches I consider Stephansdom the most outstanding, even the exterior is special with its coloured roof-tiles and the towers next to the choir, and not flanking the main facade. It is a bit of a pity you have to pay to see anything of the interior, but other churches do that too nowadays. The chancel, the Wiener-Neust\"adter Altarpiece and the tomb of Emperor Frederik III are masterpieces of gothic style wood and stone carving, unfortunately only some stained glass windows survived, or have been put in in modern times, thus the usual wow effect of such gothic art is a bit missing. \\
Second only to the masterful tombs of French Kings in St Denis and next to Roskilde, Kapuzinergruft has an absolutely amazing collection of coffins and funeral monuments to offer, far superior to the Hohenzollerngruft at Berliner Dom for example. Now Hofburg has many wings, many museums to offer: the Kaiserliche Schatzkammer contains some of the best treasures in the whole German speaking world, in fact the former German Imperial crown jewels is the most complete collection of medieval regalia in all of Europe, and absolute highlight of medieval art. There's also the actual Austrian Imperial crown, but as more modern piece it is a bit of lesser value in my opinion. Clearly the treasure does contain a lot of church items too. Another museum in the Hofburg complex is the Albertina, which is in fact a museum with two parts: the first part are state hall of Habsburg princes and their families, mostly from the 18th and 19th century (and unlike in the Imperial palaces, photos are allowed here), the second part is a Modern art museum with pieces from Monet, Renoir, Picasso, Ernst, etc). Both parts on their own are amazing, now imagine getting both of them in one ticket. Now for lovers of more traditional art, predominantly from the former Imperial collection of paintings, go to Kunsthistorisches Museum, the piece you might have heard of is Brueghel's Tower of Babylon. Another arts museum combined with Baroque state halls, and a Baroque Garden (that one is for free though), is the Belvedere Museum, where the Upper Palace contains paintings, such as Gustav Klimt's Kiss, the Lower Palace exhibits sculptures (closed for all of 2021 and maybe 2022). \\
If you think of libraries, most of those are situated in monasteries, but the most beautiful library in Vienna is the former Imperial Library, which is nowadays part of the National Library, a giant hall with lots of columns, statues, golden leaf decoration and large ceiling frescoes, one of the most beautiful libraries I know about. The zoo of Vienna is the oldest in the world, in fact it is situated on the grounds of the former Imperial summer palace of Sch\"onbrunn: besides the classical part, which alone shows old baroque architecture and symmetry, you can find Elephants, big cats such as tigers or lions, ice bears, pandas, koala's, rhinos, penguins, etc etc. Sch\"onbrunn palace suffers a bit of overcrowding, you find a bit less crowds in the final rooms of the Grand Tour usually. The palace rooms span from Baroque period of Maria Theresia to periods of the 19th century such as Franz Joseph. My personal highlights are the Great Gallery (you are allowed to take photos in that one hall), and the Vieux-Laque-Room and the Millionenzimmer (both only accessible on the Grand Tour). I had a special experience this time around as I went just on the second day of reopening after the Corona lockdown, I had the palace basically for myself - magical but most probably not able to be replicated.\\
Now the palace garden is vast and large, and largely free to visit, you can find many locals who just enjoy time there sitting by the ponds or the meadows, or doing their jogging rounds through the hills and alleys: now you have artificial ruins, several fountains, statues scattered throughout the park, but also a view point, side gardens, a palm house (one of the best I have seen in botanical gardens, although the rooftop ways had been closed), a desert house, and a large Maze, where it took me a while to find the way to the lookout stairs, so for sure something fun to do. Close to the palace is also the Wagenburg with some of the carriages (and one car) which were in use by the Imperial family up to the fall of the Monarchy in 1918.\\

As former imperial capital what is just four stars in Vienna might be like five stars in other places, but well you got to work in your own backyard too:\\
Vienna has a couple of Baroque churches, all of which are beautiful orienting themselves more on Roman Baroque than the classical style of France or England: Two domed churches are well-known, particularly Karlskirche with its great setting just next to a large reflecting pool. Karlskirche would be a five star church wouldn't some genius have thought leaving an old construction elevator up to the dome would be a good thing to do. It now obstructs the view of a significant portion of the dome which spoils the atmosphere. It does offer close view of the dome and old city with Stephansdom from the dome though, but a roof terrace view which is possible without that obstruction could have been a better alternative. Add the 8 EUR fee and you get the downgrade. Now Peterskirche is beautiful too with the dome dominating the church space, but a tad smaller than Karlskirche and a bit darker, but unobstructed. The Jesuit Church is bright colourful Baroque with many side chapels, the Franziskanerkirche is a bit darker, but I liked the idea and style a bit more. The Bernardikapelle at Heiligenkreuzerhof is a tiny but beautiful gilded Baroque gem. The stained glass window of the neogothic Votivkirche are an excellent example or the revival of stained glass art in the 19th century..\\
Unfortunately the actual state halls of the Hofburg palace are not open for view, some are used in the context of the OSCE headquarters and congress centre, the former ball rooms had been redecorated after a devastating fire, and serve now as temporary parliament chambers. Nevertheless the private quarters of Franz Joseph and Elisabeth, the last long reigning imperial couple of the mid 19th century, are virtually left unchanged in one wing. While not as sumptuous as Sch\"onbrunn or late Baroque palaces, they still give an interesting view of some of the last emperors of Austria (unfortunately no photos allowed either). Now the Staatsoper of Vienna was built in the mid 19th century. From those times one of the Foyers, the loggia, and the former Imperial Hall (now called Teesalon) survived the destructions of the war, but that still gives a great impressions of the fashion of those time, a tad less beautiful than the opera of Budapest though which was built around the same time. What is now special about Vienna's state opera: the new modern interpretation of the amphitheatre as well as new marble inlays and modern style tapestries in the side Foyers, a nice contrast but still with a fitting harmonic style. I so far cannot comment on the quality of the actual performance.\\
Now let's talk about Museums: Albertina Modern offers nice pieces from Lichtenstein, Baselitz or Warhol, as well as other  changing contemporary exhibitions. The Museum of Natural History offers a gigantic mineral collection, also many fossils, dinosaurs, but not only that, even masterpieces of the ancient Hallstatt culture are on display here, as well as some gemstones from the former Imperial Habsburg family, definitely interesting both for folks like me as well as family with young kids. The classical roman and greek artefacts in the Ephesos museum or the worldwide treasures from Central America, South East Asia, and Africa(including some of the problematic Benin Bronzes) can be found in the Neue Burg wing of Hofburg. \\

The Silberkammer in Hofburg is nice, but just gets repetitive quite quickly, a collection of gold and silver plates, chandeliers etc, each one of them really nice, but it feel more of the same already in the second or third room. There are many ticket options where you can combine it with the Kaiserappartements or Sch\"onbrunn but standalone not up with other things. I am not that amazed by horses (if you should be put that up in the highest category AND visit a show or a training performance), thus I attended the architecture tour of the Spanish Horse Riding School. You see the beautiful festive hall of the winter riding school, as well as the roof construction and the roof top view of Vienna. Seeing that construction was a highlight, and don't worry you still get close to the horses when visiting Stallburg. Now the Secession has one single nice room with the Beethovenfries, whenever I had been there all other rooms had been closed off, and the ticket price is just too much for that one (indeed nice room). Vienna has a furniture museum, partially based on old Imperial furniture from castles which had been used for other purposes, as well as furniture the new emperors might not have liked anymore. Then we got a couple of churches which are each on their own nice, but not special compared to the previous ones in category four, from Baroque (Annakirche, Kirche am Hof, Schottenkirche), to revival style (neoromanesque Franz Assisi with neobyzantine with Kaiserin-Elisabeth-Ged\"achtniskpaelle), or the gothic style Maria am Gestade. The museum of Schottenstift is nice too, the Festsaal and Library are from the 1830s, quite nice too (although the Festsaal is another version of the Albertina festival hall by the same architect), but maybe a bit expensive. Usually the Baroque Hall of Vienna's old city hall is closed off, by chance it had been open when I visited, and I did make use of it. The hall and the adjacent rooms are quite nice to see, but most probably they are closed off should you pass by. Same could be true for the beautiful staircase of Palais Daun-Kinsky, although I read online that the stairs are often open and accessible.\\

Augustinerkirche in Hofburg is the former imperial church, kind of plain though if you ask me, with a nice altar piece but otherwise a bit underwhelming. Minoritenkirche, a gothic style church, has a couple of nice windows and a copy of Da Vinci's Last Supper, but nothing much more. Next to the Kapuzinergruft Kapuzinerkirche is just a small shadow of a beautiful church. Palais Lobkowitz is a speciality museum, listing history of theatres, old puppets and marionettes and costumes, masks can be found there, for sure something interesting for theatre lovers. The Eroica Hall in the middle of the museum is nice too, the museum has items from re-known artists such as Rubens, Boticelli or Hieronymus Bosch (his last judgement is the only altar I really enjoyed there though), but just not on the level of other arts museums in Vienna. Similarly for the Globe museum, telling the stories of how to produce maps, globes, as well as globes of zodiacs or the sky, or moon globes, once again rather for lovers of globes. Now at Belvedere 21 they had an exhibition of Beuys, in fact a huge collection and variety of his art pieces. Beuys is considered one of the most interesting contemporary artists, but it is just not my thing. Now protestant churches are always a bit more solemn and ``simple'' compared to catholic churches, in fact in Vienna they are still comparably richly decorated, but just not like many other churches here. The Dommuseum is small and just not on the level of what I would have expected from such a beautiful church like Stephansdom, maybe some pieces were transferred to the Imperial Treasury which does have a spectacular exhibition of religious items too.\\

With so many churches to see there are some, which might just be alright in other places, but they just don't hold up at all next to their neighbours etc: the parish church of Kagran up in the north, actually an old church but just nothing much there to see. The Johann-Nepomuk-Kirche bei Nestroyplatz is just a normal church, a large mural in the choir, more a classicist style otherwise, but well just normal. The Malteserkirche is a tad small, and being just between Stephansdom \& Karlskirche doesn't help to raise its status. Deutschordenskirche is close to that area too, has a couple of shields on the wall, but otherwise a tad empty.\\

%five, four, two, one stars are done

Vienna: \\
Five Star Attractions (12): Stephansdom***** (paying to get closer to the altar pieces though), Kapuzinergruft*****, Schloss Sch\"onbrunn***** (Palace: Grand Tour***** no crowds), Sch\"onbrunn Palace Gardens***** (Maze*****, Gloriette****, Kronprinzengarten***, Palmenhaus*****, W\"ustenhaus***, Wagenburg****),) Hofburg: National Library*****, Hofburg: Kaiserliche Schatzkammer (Imperial Treasury)*****, Tiergarten Sch\"onbrunn*****, Belvedere***** (Oberes Belvedere*****, Unteres Belvedere*****, Belvedere Gardens****), Nationalpark Donau-Auen (Danube Wetlands)*****, Hofburg: Albertina***** (State Rooms*****, Museum****),  Kunsthistorisches Museum*****, Tiergarten Sch\"onbrunn*****\\

Four Star Attractions (12): Peterskirche****, Jesuit Church****, Votivkirche****, Franziskanerkirche****, Hofburg: Kaiserappartements****, Hofburg: Weltmuseum (World Museum)****, Karlskirche****, Albertina Modern****, Naturhistorisches Museum**** , Hofburg: Ephesos Museum****, Bernardikapelle at Heiligenkreuzerhof****, State Opera****\\ 

Three Star Attractions (13):  Michealskirche***, Schottenstift*** (Schottenkirche***, Festival Hall and Library***, Museum****), Kirche am Hof***, Old City Hall*** (with Barocksaal), Hofburg: Silver Chamber***,  Secession with Beethovenfries***, Stadtpark (City Park)***, Franz von Assisi Church (with Kaiserin-Elisabeth-Ged\"achtniskpaelle)***, Hofburg: Spanish Riding School with Roof Top*** , Annakirche***, M\"obelmuseum***, Maria am Gestade***, Palais Daun-Kinsky: Staircase***\\

Two Stars (10): Hofburg: Augustinerkirche**, Minoritenkirche**   Deutschordenskirche**, Palais Lobkowitz** (Theatre Museum**, Gallery of Academy of Arts***), Palais Mollard: Globenmuseum**, Belvedere 21 (Beuys Exhibition)**, Protestant Church** (interior), Lutheran Church** (interior), Dommuseum**, Kapuzinerkirche**\\

One Star (3): Johann-Nepomuk-Kirche*, Kagran St Georg*, Malteserkirche*\\

Zero Star: None

\section{May 16: Schloss Hof}
\label{2021SchlossHof}

Engelhartstetten: Schloss Niederweiden*, Schloss Hof**** (Schloss***, Park*****)

\section{May 22: Golling an der Salzach \& Salzburg}
\label{2021GollingSalzburg}

OK the weather of May 2021 wasn't on the bright side with frequent rain showers and cloudy days, but finally after the nightly curfew had been lifted I wanted to get a bit out of Vienna into nature, thus the region of Salzburg was my first place to visit. Being my usual self I got up at 4 am to make it to the train to Salzburg comfortably and then going south into the alps. Once I got out in Golling the clouds were hiding the mountain tops, nice to see, but the rain was not that amazing. Anyway I made it to the waterfalls just a bit after they opened at 9 am, and during my visit (in rain) I was the only one around. In Golling the Schwarzbach drops in two big waterfalls and a couple of cascades by about 79 metres. The trail is alright with lots of stairs and a couple of bridges which can be quite humid, not only from the rain such as in my case but also from the water vapour of the waterfalls. The lower fall is particularly beautiful, since it widens up at the base in several water patterns. The trail leading up offers several perspectives of the fall before it crosses over several cascades. At that point one can see the base of the upper waterfall which hides itself within rocks otherwise, only when one crosses the bridge and climbs up a couple of 10 metres from another bridge one gets a full view of the upper fall. Another flight of stairs later one reaches the spring of the creek, which starts just a couple of metres away from the upper fall. Altogether very impressive, although I did hurry a bit due to the rain, so try to visit it in a bit of sun. The foggy/cloudy setting still looks great on photos, but getting real wet wasn't that much fun.\\
And onwards back north to the southern tip of Salzburg by Schloss Hellbrunn. While the castle itself was still closed due to Covid19 regulations, the park and the water fountains could be visited. While water and trick fountains had been en vogue in Baroque times, once they went out of fashion they were removed from the parks in almost all places. Thus typically the places are quite crowded and popular where they can still be found nowadays. Once again we were told that on a usual day Hellbrunn has about 10 times the visitors of my visit, thus the experience might be vastly different then. I did enjoy the audio tour, also the trick fountains in action as well. I did not only enjoy the fountains but also the grottoes on the ground floor of the castle, as well as the mechanical theatres which are part of the park too. Then I walked through the forest area of the park (which can be visited for free). The Stadtaussicht has a nice view of Hohensalzburg Fortress, the Watzmannblick suffered from too many clouds, thus the Watzmann massif hid on that very day, but the Steintheater, a artificial theatre set up by huge blocks of stone was worth the walk alone. Thus Hellbrunn is definitely a place which can go on your Salzburg itinerary.\\
And then it was finally time to get over to old town, which is another UNESCO world heritage site. But we reach the utter absolute disappointment of Salzburg first: The new residence. This place houses typically exhibitions in beautiful state rooms. For whatever reason they had the whole floor with the state rooms closed off and the same ticket price as ever. The exhibit regarding the Salzburg Festival was very poor too, mainly just panels to read with very few exhibits. I was very disappointed. Then I walk over the squares of old town with short visits of Michaelskirche and Kollegienkirche, having a short snack on the Market Square. I was particularly pleasantly by Franziskanerkirche which has a pretty dark romanesque nave which opens up to a wide bright gothic style choir hall, whose chapels have been refurbished in Baroque style. Another Baroque style gem with lots of stucco, large paintings, etc is the arch abbey of St Peter. Then the highlight of Salzburg: the beautiful Old Residence with the Arch Bishop's State Rooms. Amazing baroque paintings, tapestries, large frescoes, the odd modern art pieces here and there though. Not really fitting the context unfortunately, but unlike in other places I did like the sculptures in fact. Thus maybe they should have been placed in other rooms in their own right. Now part of the itinerary is also the cathedral museum, which is small but with some precious pieces. The oratory of the bishop is usually very nice to see, this time it had been inexplicably obstructed by a giant mirror wall dividing the room into two parts (why just why?). Still onwards to the cathedral: one of the largest Baroque churches north of the alps, unlike many other Baroque churches in Austria, this one is more similar to the classic Baroque of France or England. \\
The most visited place in Salzburg is the Fortress of Hohensalzburg, one of the best conserved large medieval castles of the whole continent. And unlike in other places at least parts of the rooms, the so-called F\"urstenzimmer, are largely conserved in their original state. Since you have to pay extra for these rooms only a couple of people opted for that it seems, at least I had all three rooms to myself for quite a while. The gold leaved wood carvings, ceilings, columns, medieval shields on the beams etc are some of the best from original late medieval gothic period. I know those are only three rooms, so might sounds only little for a steep price, but just consider those rooms are about 600 years old, and only a handful of those secular rooms are still conserved in such a good state elsewhere. The view of old town and the mountains is nice too from up of the castle. \\
I had finished my program much faster than anticipated, thus I had time to improvise. First I visited the close-by cemetery by St Peter with a couple of chapels, also some hidden in the hillside (the so-called catacombs). Then I decided first to try to get a good view of old town from the Capuchin hill. On my way to the view point I passed St Johannes im Berg and the Capuchin Church itself (not that amazing though). The view was pretty nice, maybe you could do a snack stop up there. On my way to the train station I walked past Dreifaltigkeitskirche (Holy Trinity Church) and Mirabellpark - places of typical Baroque, also the stair case of Mirabell was nice, but nothing I would go out of my way for. I still managed to just get on a train an hour earlier than I had planned, thus I just arrived back home just in time for the Eurovision Song Contest 2021 (priorities I know, I know).\\

Golling an der Salzach: Waterfalls*****\\
Salzburg: Schloss Hellbrunn Wasserspiele \& Park with Steintheater*****, Alte Residenz***** (State Halls*****, Museum St Peter****, Wunderkammer***, Residenzgalerie****, Cathedral Museum with Oratories****), Neue Residenz, Michaelskirche**, Kollegienkirche***, Franziskanerkirche****, St Peter****, Dom*****, Festung Hohensalzburg***** (F\"urstenzimmer*****), St Peter Cemetery*** (Catacombs**, Mariazellkapelle***, Margarethenkapelle***), St Johannes im Berg**, Capucin Church**, Holy Trinity Church***, Schloss Mirabell (Donnerstiege only) with Gardens***

\section{May 24: Hallstatt}
\label{May2021Hallstatt}

After a one day intermezzo of visits in Vienna (State Opera \& Horse Riding School) it was time for my first visit to the Austrian State of Upper Austria, jumping on the first train out of Vienna once again. Hallstatt is very popular with South Asian tourists, since it features prominently in TV series (I heard it is a series in South Korea). But due to Corona restrictions none of those were expected to be around, but with a higher influx of locals (such as myself). But none of the buses had been full, but people getting on the train in Upper Austria started already their private drinking and hiking parties in the train. The train ride from Linz is already very nice past the mountain scape by Traunsee. I can easily understand why Franz Joseph and Elisabeth enjoyed their summers in the region of Bad Ischl. And then I reached Steeg and made my way to enjoy the view of Hallst\"atter See by the outflow of the Traun before getting on the first of two buses to bring me to Hallstatt Lahn. There I jumped on the cable car up to Salzberg. The view from the Skywalk View point up their is magical with the Dachstein massif all around the lake (although I will never understand why it is the current fashion to built those ugly pointy over the mountain platforms which add next to nothing to the experience itself. Then I walked the 15 minutes to the Salt Mine, put on the purple overall and joined the tour of the old mine tunnels. The Salt Mine is still in continuous use after over 7000 years of mining. Now the two slides were fun, the multimedia projection over the salt lake was neat too, but was it worth 36 EUR, not really, but at least I've done it now, although which Salt Mine can claim to host the oldest wooden staircase of the continent (if not the planet).\\
 Instead of taking the cable car down I opted for the trail down to the village. Besides the obvious pretty views of the mountain lake itself the great waterfalls of the M\"uhlbach were the cherries on the cake. The creek falls down over several hundreds of metres in a series of several large waterfalls, really great to see (the view of the last big falls is a bit spoilt by the ugly-ass parking lot). Once down in the village I saw the catholic church (nice late gothic wood carved altar pieces), decided to skip the Bone House (at least 45 minute waiting time, and I doubt it would be as impressive as those of Rome or Milan), had a short peak into the protestant church and got myself a snack on the market square.\\
  And then it was time for hike number two down into the Echerntal along the Waldbach. The first large waterfall which one passes on that trail is the Schleierfall further into the valley I passed several small cascades with large rocks until I reached the Waldbachstrub wall, where the Waldbach meets the Lauterbach and one can admire four waterfalls. At the time of my visit all waterfalls were carrying quite a bit of water, that much water that on the upper view point the waterfall showered me with its vapour. I definitely recommend you spent these 60-120 minutes (depending on your walking speed) to enjoy these waterfalls. On the way back I passed by other spots and the Gletschergarten. I still had time left to visit the Welterbemuseum, there one can admire artefacts from the Hallstatt period, both from the Salt Mine and the tombs up on Salzberg.\\
   And last but not least time for a boat ride. I had anticipated I would have absolutely no time for a boat tour, but seems my hiking speed was faster despite the long break of any alpine hikes. The boat ride goes in a round trip to Obertraun and back to Hallstatt offering beautiful views of the Dachstein mountains. Maybe once Covid19 dies down, you can also enjoy drinks on the boat again, else enjoy the view masked up. Still time to go I had some local soup and beer before jumping on a bus and three trains plus a metro ride back to Vienna (it does take that long as it sounds, a bit more than 4 hours, but the trip and the Alps, and the views were definitely worth the hassle).\\

Hallstatt: Salt Mine****, Skywalk View Point*****, Trail Salt Mine down along M\"uhlbachfalls*****, Catholic Church****, Protestant Church**, Echerntal hike with Waldbach, Waldbachstrub waterfalls \& Schleierfall*****, Boat Ride round trip to Obertraun****, World Heritage Museum***

\section{May 30: Klosterneuburg}
\label{Klosterneuburg}

Klosterneuburg is a neighbouring town of Vienna, where an old large monastery is located. While the monastery has roots dating back to middle ages, the church interiour was completely remodelled in Baroque style. Emperor Charles VI of Austria wanted to built his summer palace here in an Austrian version of the El Escorial (in fact the cafe in the monastery is called El Escorial). After his untimely death his daughter Maria Theresia decided to not continue the building campaign and thus less than one fourth of the whole project had been realised. Some halls such as the Sala Terrana are half finished, only a handful of rooms of the Emperor's wing give you an idea what could have become of this place, the emperor himself spent one single night in these quarters. The church itself is the typical baroque style of Austria with tons of stuccos, one large nave with many frescoes and one large nave with side chapels. The largest treasure of the monastery can only be seen with a guide, a medieval seven-branched wooden candelabrum, and a large altarpiece with 52 golden enamel plates which had been the decoration of the former pulpit which was turned into an altar after a large fire in the 14th century.

Klosterneuburg: Stift***** (church*****, cloister and altar of Verdun*****, Kaiserzimmer****, Treasury****, Museum****)





