\chapter{Preamble}

When you hear about someone's travel you often hear how awesome it was and amazing (or the opposite: everything was bad, from the hotel, the food in restaurants, overcrowded beaches etc). Unlike those stories, trips are in general a fun time to see or discover something interesting while spending time friends or family merged with unfortunate things like public transport on strike, broken down cars, getting lost, overpriced sights, and other mishaps. You won't only hear about the sunny days, beautiful mountain sceneries, deserted incredible beaches, or days without smog in the huge metropolis, but also about days getting completely soaked in pouring rain, flooded metro stations. The current version takes you to four continents (no Australia, Antarctica or South America as of yet), obviously still open for that to happen in future updates. You will get to hear a huge amount about the beauty of places and the fun you can experience in about 700 places in close to 40 countries (and still counting). What is your take on a comment along the lines of: the Vatican is not a real country? or countries you have only been at an airport don't count?\\

Now I also have a point system going on, which is of course subjective, depending on the type of visit, expectations, changes of the visits: I have been in several place more than once, but if a tour changes from over an hour to just 15 minutes going along the same route, then you know something is wrong. On the other hand there have been places where I expected a lot, was disappointed, lowered my expectations. Going in with these expectations I started to enjoy that place again. It also depends what you did the days before, standalone a place might be great, but just not as great as something else, so you maybe downvote it just by comparison, while by its own you might have been wow'ed by it. Anyways the point system:

Five Star Attractions: essentials, you should really do that\\
Four Star Attractions: great to do, but not essential\\
Three Star Attractions: in the context of the place this is the typical good bread \& butter you get here\\
Two Stars: step in if you have time, some disappointing aspects, sometimes I am also just bored since it is not my thing I enjoy to do\\
One Star: disappointing, maybe step in if you just in the area, not for spending many time there\\
Zero Star: just avoid, to get to that place, something must have gone really wrong, or it was amazingly over expensive\\
